Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series

### 2023-02-23 Manuscript/manuscript.tex
2/16 Notes
commented on line width
Manuscript Update

\begin{abstract}
Block bootstrap is a method that is useful for estimating a parameter of a time
series. Theoretically, the method will work perfectly given an infinitely large sample of the time series.
It is necessary to know how large of a finite sample is required to for block bootstrap estimation to work. 
Before this study, there have been no investigations into this problem in the literature. The aim of this study 
is to answer this question by simulating replications of block bootstrap interval estimations of a parameter of a time series, 
and recording the rate at which the parameter is recovered by each replicate interval. 
The sample length required for acceptable performance is unsurprisingly found to be dependent 
on the type of interval construction and the series' level of temporal dependence.

@@

\jy{Practice my writing tips on latex (e.g., keep line width under 80; use
  double blank lines to separate paragraphs; etc.):
\url{https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}

@@

While the aforementioned studies have looked into the necessary sample size for various bootstrap methods, 
the goal of this study is to find a threshold or range of sample sizes at which block bootstrap 
is an effective method for estimating a parameter specifically in the context of a time series. 
The method can be considered effective if approximately 1 - $\alpha$/2 \% of 1 - $\alpha$/2 \% of confidence intervals 
created from samples of the same size recover the parameter. This study will focus on estimating parameters of an 
AR(1) process with two types of block bootstrap confidence intervals from the literature, \citep{diciccio1996bootstrap}  \citep{rice2006mathematical} 
which is reviewed in Section 2. Section 3 offers an explanation of the simulation design and results. 
Section 4 discusses the results and how these findings could be useful.

@@

Both of these intervals work well when attempting to recover the mean and standard deviation of a temporally dependent process, 
but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals 
$\hat{\theta}_{n}$. To do this, the distribution $\delta^*$ should be considered. A percentile interval 
centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\]

%A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\] An alternative is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] which is equivalent to: \[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] and therefore is also equivalent to: \[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.

This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
%A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: \[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\] An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form: \[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]

@@

%The central objective of the study was to assess what sample size is necessary for the the block bootstrap method to estimate a parameter of an autoregressive process. The method will work better as the sample size goes to infinity, but the goal is to see what is the smallest sample size that is acceptable. The sample size is acceptable if many 1 - $\alpha$/2 confidence intervals for that sample size recover the parameter at a rate of 1 - $\alpha$/2 \%. In the previous section, the procedures for creating three types of confidence interval of a parameter using the block bootstrap method are described.

%These procedures are applied to a simulation of an autoregressive integrated moving average (ARIMA) process to create three confidence interval of certain parameters (the mean, the AR(1) coefficient, the MA(1) coefficient, the standard deviation, etc.).

Base R has a built in function arima.sim that allows one to simulate an AR(1) process, for which one can set the theoretical $\phi$. 
By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1. 
For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1. 
The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:

\[X_{t} = \epsilon_{t} + \phi X_{t-1};\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1});\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\]
\[\sigma^2_{x}(1 - \phi^2) = 1;\]
\[\sigma_{x}\sqrt{1 - \phi^2} = 1.\]

The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap. 
$\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.

As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. 
This method can be simulated with the tsboot function from the boot R package. In this study, $\theta$ is composed of the target 
parameters $\mu = 0$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, two types of block bootstrap 95\% confidence intervals 
can be constructed for each target parameter: $CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.

Each of these 6 intervals either recovers $\theta$ or does not. Remember that 95\% of many of a certain type of 95\% confidence intervals 
constructed from samples of the same $n$ should recover $\theta$. To see if this is generally or approximately the case, one can run 
1000 replications of the block bootstrap procedure, and for each interval-$\theta$ pair, the rate at which that type of interval recovers 
$\theta$ can be recorded. The coverage rate is, of course, a point estimate of a proportion, so a 95\% confidence interval of this coverage proportion 
(with $n_{CI} = 1000$) can be constructed, and if the proportion .95 is included in the interval, the block bootstrap method is likely working well.

If $\theta$ is not covered at that $n$, a larger sample size must be necessary. $n = $100, 200, 300, 400, and 500, 600, 700 were used in this study. 
Remember that the goal is to find the smallest $n$ which is sufficient for proper coverage.

%For all simulation studies, but $\mu$ and $\sigma_{x}$ can be kept constant, but increasing temporal dependence factors such as AR and MA Coefficients can make block bootstrap less effective in estimation, so its impact on the method's performance should be analyzed. For a certain variation of an AR(1) process, block bootstrap 95\% confidence intervals for each of 3 parameters ($\mu$, $\sigma_{x}$, and the autocorrelation function$\rho$) can be replicated for 1000 simulated samples of a certain length. For each individual confidence interval, it can be recorded whether or not the interval includes the true parameter. The coverage rate, or the proportion of intervals that include the true parameter, can then be recorded. If the parameter is being properly estimated by the block bootstrap, the coverage rate should reflect this by being close to the confidence level of 95\%. If this is not the case, the method is not working as well as it should. The width of the confidence interval for each replication is dependent on the variability of the parameter of the time series. If the interval is on average not wide enough to capture the parameter at the expected rate of 95\%, it indicates that the variability of the parameter is underestimated. If the interval is too wide and captures the parameter at a rate above 95\%, it indicates that the variability of the parameter is overestimated. Since the coverage rate is a proportion based on 1000 independent binary outcomes (the interval recovers the parameter or it doesn't), a 95\% confidence interval of the coverage rate for each parameter can also be created. The inclusion of .95 in the interval indicates that the block bootstrap method is working well for its respective parameter. If this is not the case for this sample length, the procedure can be conducted again with a larger sample length. This can be repeated until the method is determined to be working acceptably, meaning that .95 is included in the 95\% confidence interval of the coverage rate of the parameter.

%1000 replicates of length-n random samples of an AR(1) process with theoretical $\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1 were simulated using R. For each of three target parameters ($\mu$ = 0, $\sigma_{x}$ = 1, and $\theta$ = 0.1, three types of block bootstrap (with block length l) confidence intervals (percentile, empirical, and BCA) were constructed for each replicate sample. The statistic used to estimate $\mu$ is the sample mean $\bar{x}$, the statistic used to estimate $\sigma$ is the sample standard deviation $S^2$, and the statistic used to estimate $\theta$ is the auto-correlation function of the sample. For each of these nine categories of confidence intervals, the coverage rate of its respective parameter was computed, along with a 95\% confidence interval of the proportion given 4000 trials. For a certain variation of the process, the study was repeated for n = 125, 1000, 3375, and 8000. The only parameter of the process that was varied was $\theta$, and 0.1, 0.3, and 0.5 were the values used.

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.4}
  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as 
  low as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, so one can 
  expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, 
  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear pattern of deterioration of coverage.}
  \label{fig:plot_n.4}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.2}
  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as $n = 100$. Both intervals seem to cover $\sigma$ generally well, 
  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
  and this is true as low as $n = 200$.  $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_n.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
  $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but there is no clear pattern of deterioration of coverage, 
  so one can expect that increasing $n$ will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ seems to cover 
  $\phi$ generally well at $n = 400$, but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the method's performance seems to improve as $n$ increases.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as $n = 300$. Both intervals seem to cover $\sigma$ generally well, 
  although $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low as $n = 400$. 
  $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there is no clear sign of coverage deterioration, so one can expect that increasing $n$ 
  will eventually result in proper coverage of $\sigma$. $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of coverage, 
  and this is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.4}
\end{figure}

Only $CI_{\hat{\theta}_{n}}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that this interval 
should be used as opposed to $CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. As expected, a higher $\phi$ demands a 
larger $n$ to estimate all parameters, but a negative $\phi$ may only require a lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, 
$n = 100$ was sufficient to recover $\mu$ at a rate of approximately 95\%.

@@

The motivation for the study is the idea that block bootstrap procedure will perfectly estimate a parameter of a time series given an infinitely large sample. 
The goal for this study was to find what is a good enough finite sample length for block bootstrap estimation to recover the parameter of a 
time series at an acceptable rate. Assuming that $CI_{\hat{\theta}_{n}}$ is used (as it was found to work better overall, especially when estimation $\phi$), 
the results of this study suggest that even for estimating $\mu$, an $n$ of around 500 may be necessary if $\phi$ is unknown. 
An $n$ of around 400 may be necessary to estimate $\sigma$ is $\phi$ is unknown. If $\phi$ is already known, 
a lesser $n$ may be adequate to estimate these parameters. When $\phi$ was negative, 
a $n$ of around 100 was sufficient to estimate $\mu$. However, in real world applications, $\phi$ is more commonly found to be positive, 
so a larger $n$ is more likely to be necessary. Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. 
This information could prove to be useful for researching using block bootstrap estimation of time series in domains such as econometrics. 
Future studies could investigate if there are types of block bootstrap intervals that can be constructed that 
would more appropriate recover the parameters of a time series. One could also investigate the $n$ needed to 
make inferences about other forms of serially dependent data such as an MA process.

>>>>

\begin{abstract}
Block bootstrap is a method that is useful for estimating a parameter of a time
series. Theoretically, the method will work perfectly given an infinitely
large sample of the time series. It is necessary to know how large of a finite
sample is required for block bootstrap estimation to work. Before this study,
there have been no investigations into this problem within the literature. The
aim of this study is to answer this question by simulating replications of
block bootstrap interval estimations of a parameter of a time series, and
recording the rate at which the parameter is recovered by each replicate
interval. The sample length required for acceptable performance is
unsurprisingly found to be dependent on the type of interval construction and
the series' level of temporal dependence.

@@

\jy{Practice my writing tips on latex (e.g., keep line width under 80; use
  double blank lines to separate paragraphs; etc.):
  \url{
https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html}}

\jy{turn on the column number mode of your editor. Keep the width to under 80.}

@@

While the aforementioned studies have looked into the necessary sample size
for various bootstrap methods to make inferences about various types of data,
the goal of this study is to find a threshold or range of sample sizes at
which block bootstrap is an effective method for estimating a parameter
specifically in the context of a time series. The method can be considered
effective if the rate at which confidence intervals created from samples of
the same size recover the parameter is approximately equal to the nominal
confidence level. This study will focus on estimating parameters of an AR(1)
process with two types of block bootstrap confidence intervals from the
literature \citep{diciccio1996bootstrap} \citep{rice2006mathematical}. How
these intervals are constructed as well as the general procedure for block
bootstrap parameter estimation is reviewed in Section 2. Section 3 offers an
explanation of the simulation design and results. Section 4 discusses the main
takeaways from the results, how these findings could be useful, and possible
future explorations.

@@

Both of these intervals work well when attempting to recover the mean and
standard deviation of a temporally dependent process, but their coverage of
the temporal dependence deteriorates as $n$ increases. A potential solution to
this issue is to center the intervals $\hat{\theta}_{n}$. To do this, the
distribution $\delta^*$ should be considered. A percentile interval centered
around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2},
  \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
This centering procedure can also be applied to a BCA interval. A BCA interval
centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the
form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1},
  \hat{\theta}_{n} + \delta^*_{\alpha_2}].\]

@@

Base R has a built in function arima.sim that allows one to simulate an AR(1)
process, for which one can set the theoretical $\phi$. By default, the mean of
the process $\mu$ is 0 and the standard deviation of the error term
$\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard
deviation of the process $\sigma_{x}$ should be controlled at 1. The
observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
\begin{align}
X_{t} &= \epsilon_{t} + \phi X_{t-1};\\
Var(X_{t}) &= Var(\epsilon_{t} + \phi X_{t-1});\\
\sigma^2_{x} &= \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\\
\sigma^2_{x}(1 - \phi^2) &= 1;\\
\sigma_{x}\sqrt{1 - \phi^2} &= 1.
\end{align}
The experimental factor of this study was $\phi$, as the temporal dependence
affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a
standard normal distribution)$, 0.2, and 0.4$ were used in this study.

As described in the last section, the block bootstrap method can be used to
estimate a parameter $\theta$ of an AR(1) process. This method can be
simulated with the tsboot function from the boot R package. In this study,
$\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and
$\phi$. The sample mean $\bar{x}$ can be used as the statistic to estimate
$\mu$, the sample standard deviation $S_x$ can be used as the statistic to
estimate $\sigma$, and the autocorrelation function of the sample at lag 1
$\rho_1$ can be used as the statistic to estimate $\phi$. In the R
implementation, these three statistics are incorporated into a function that
will apply each statistic to the original sample and to each bootstrapped
pseudo-sample. From a sample of length $n$, two types of block bootstrap 95\%
confidence intervals can be constructed for each target parameter:
$CI_{\hat{\theta}_{n}}$ and $CI_{BCA, \hat{\theta}_{n}}$.

Each of these 6 intervals either recovers $\theta$ or does not. Remember that
95\% of many of a certain type of 95\% confidence intervals constructed from
samples of the same $n$ should recover $\theta$. To see if this is
approximately the case, one can run 1000 replications of the block bootstrap
procedure, and for each interval-$\theta$ pair, the rate at which that type of
interval recovers $\theta$ can be recorded. The coverage rate is, of course, a
point estimate of a proportion, so a 95\% confidence interval of this coverage
proportion (with $n_{CI} = 1000$) can be constructed, and if the proportion
.95 is included in the interval, the block bootstrap method is likely working
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased. $n =$
100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.4}
  \caption{At $\phi = -.4$, both intervals covered $\mu$ correctly as low as
    $n = 100$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as
    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but there
    is no clear pattern of deterioration of coverage, so one can expect that
    increasing $n$ will eventually result in proper coverage of $\sigma$.
    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration, and this
    is true as low as $n = 200$. $CI_{BCA, \hat{\theta}_{n}}$ greatly
    under-covers $\phi$, and there is a clear pattern of deterioration of
    coverage.}
  \label{fig:plot_n.4}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.2}
  \caption{At $\phi = -.2$, both intervals covered $\mu$ correctly as low as
    $n = 100$. Both intervals seem to cover $\sigma$ generally well, although
    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
    coverage, and this is true as low as $n = 200$.
    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a
    clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_n.2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, both intervals covered $\mu$ correctly as low as
    $n = 500$. $CI_{\hat{\theta}_{n}}$ seems to cover $\sigma$ well as low as 
    $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ slightly under-covers $\sigma$, but
    there is no clear pattern of deterioration of coverage, so one can expect
    that increasing $n$ will eventually result in proper coverage of $\sigma$.
    $CI_{\hat{\theta}_{n}}$ seems to cover $\phi$ generally well at $n = 400$,
    but $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\phi$, although the
    method's performance seems to improve as $n$ increases.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, both intervals covered $\mu$ correctly as low as
    $n = 300$. Both intervals seem to cover $\sigma$ generally well, although
    $CI_{BCA, \hat{\theta}_{n}}$ has somewhat lower coverage rates.
    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
    coverage, and this is true as low as $n = 200$.
    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, but there is no
    clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$, both intervals seem to cover $\mu$ generally well
    as low as $n = 400$. $CI_{\hat{\theta}_{n}}$ covers $\sigma$ well as low
    as $n = 400$. $CI_{BCA, \hat{\theta}_{n}}$ under-covers $\sigma$, but
    there is no clear sign of coverage deterioration, so one can expect that
    increasing $n$ will eventually result in proper coverage of $\sigma$.
    $CI_{\hat{\theta}_{n}}$ covers $\phi$ well with no deterioration of
    coverage, and this is true as low as $n = 200$.
    $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with a clear
    coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.4}
\end{figure}

As shown in the above figures, only $CI_{\hat{\theta}_{n}}$ managed to solve
the deterioration problem with respect to recovering $\phi$, indicating that
this interval should be used as opposed to the more complex
$CI_{BCA, \hat{\theta}_{n}}$ when estimating $\phi$. Increasing $n$ will not
fix the performance of $CI_{BCA, \hat{\theta}_{n}}$ because the assumption that
the coverage rate will approach an upper limit of .95 as $n$ increases is
invalid. As expected for $CI_{\hat{\theta}_{n}}$, a higher $\phi$ demands a
larger $n$ to estimate all parameters, but a negative $\phi$ may require a
lesser $n$. For example, for both $\phi = 0.2$ and $0.4$, $n = 100$ was
sufficient to recover $\mu$ at a rate of approximately 95\%.

@@

The motivation for the study is the idea that block bootstrap procedure will
perfectly estimate a parameter of a time series given an infinitely large
sample. The goal for this study was to find what is a good enough finite
sample length for block bootstrap estimation to recover the parameter of a
time series at an acceptable rate. Again, this relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $CI_{\hat{\theta}_{n}}$, whereas
$CI_{BCA, \hat{\theta}_{n}}$ exhibited coverage deterioration as $n$
increased. When using $CI_{\hat{\theta}_{n}}$ and $\phi$ is unknown, the
results of this study suggest that an $n$ of around 500 may be necessary to
estimate $\mu$, and an $n$ of around 400 may be necessary to estimate
$\sigma$. If $\phi$ is already known, a lesser $n$ may be adequate to estimate
these parameters. When $\phi$ was negative, a $n$ of around 100 was sufficient
to estimate $\mu$. However, in real world applications, $\phi$ is more
commonly found to be positive, so a larger $n$ is more likely to be necessary.
Lastly, to estimate $\phi$, an $n$ of around 400 may be necessary. This
information could prove to be useful for researching using block bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap intervals
constructions that would more appropriately recover the parameters of a time
series. One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as an MA process.
